On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-07 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt

Response for Referee #1
---

1. (p. 1, L17-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon. However, to avoid any confusion, we have removed discussion of Runge's problem from the text.

@@

14. (Algs. 2 and 5 ...) Thank you. We have clarified that we refer to the set of all multinomial combinations of basis vectors up to a predefined maximum order.

15. (Algs. 2 and 5 ...) Thank you. We have corrected these lines to reference epsilons.

16. (p. 3, L60) The current description of \lambda_{bulk} seeks to communicate the presense of the constant term.

17. (p. 5, L3-4) We have sought to clarify the text to minimize confusion.

### 2019-02-07 docs/mvfits_paper/mvf.tex
now avoiding Runges problem all together to hopefully speed thigs up!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %
  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries. One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes. Here, we present new phenomenological methods to model the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics). In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively. GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon. GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit. GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$. We discuss the potential use of these models in current and future gravitational wave signal modeling.
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order (e.g. the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).

@@

Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a variety of problems where polynomial interpolation is insufficient.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %
  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries. One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes. Here, we present new phenomenological methods to model the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics). In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively. GMVP is used to develop a model for QNM frequencies that explicitly enforces consistency with the extremal Kerr limit. GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$. Both models are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes. We discuss the potential use of these models in current and future gravitational wave signal modeling.
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order.

@@

Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a variety of problems where polynomial regression is insufficient.
